target_offtarget

### 2025-01-30 manuscript_figures.Rmd
update Figure 3

dedup_reads <- 
  dedup_viral_reads |>
  filter(Background.sample != "Neg_control") |>
  filter(Background.sample != "Msp_p6") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(count),
    colour = genus
  )) +
  geom_point() +
  geom_smooth(aes(group = genus, linetype = genome_structure), se = FALSE) +
  facet_grid(target ~ Background.sample, labeller = as_labeller(facet_names)) +
  theme_few() + 
  scale_x_log10() +
  ylab("Log (Viral Reads)") + 
  xlab("Log (Viral load)") + 
  scale_color_manual(values = cols) +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 30, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  )

dedup_prop_viral <-
  dedup_viral_reads |>
  filter(Background.sample != "Neg_control") |>
  filter(Background.sample != "Msp_p6") |>
  ggplot(aes(x = Viral.load, y = prop_viral, colour = genus)) +
  geom_point() +
  geom_smooth(aes(group = genus, linetype = genome_structure), se = FALSE) +
  facet_grid(target ~ Background.sample, labeller = as_labeller(facet_names)) +
  theme_few() + 
  scale_x_log10() +
  scale_y_log10() +
  ylab("Proportion of viral reads") +
  xlab("Log (Viral load)") + 
  scale_color_manual(values = cols) +
    theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 30, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  )

dedup_prop_all <-
  dedup_viral_reads |>
  filter(Background.sample != "Neg_control") |>
  filter(Background.sample != "Msp_p6") |>
  ggplot(aes(x = Viral.load, y = prop_total, colour = genus)) +
  geom_point() +
  geom_smooth(aes(group = genus, linetype = genome_structure), se = FALSE) +
  facet_grid(target ~ Background.sample, labeller = as_labeller(facet_names)) +
  theme_few() + 
  scale_x_log10() +
  scale_y_log10(limits=c(5e-8,1)) +
  ylab("Proportion of total reads") +
  xlab("Log (Viral load)") + 
  scale_color_manual(values = cols) +
    theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 30, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  )

>>>>

dedup_reads <- 
  dedup_viral_reads |>
  filter(Background.sample != "Neg_control") |>
  filter(Background.sample != "Msp_p6") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(count),
    colour = genus
  )) +
  geom_point() +
  geom_smooth(aes(group = genus, linetype = genome_structure), se = FALSE) +
  facet_grid(target ~ Background.sample, labeller = as_labeller(facet_names)) +
  theme_few() + 
  scale_x_log10() +
  ylab("Viral Reads") + 
  xlab("Viral load (gc/ml)") + 
  scale_color_manual(values = cols) +
  scale_linetype_manual(values=c("solid", "dotted"))+ 
  theme(
    axis.title.x = element_text(size = 12),
    # axis.text.x = element_text(angle = 30, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  )

dedup_prop_viral <-
  dedup_viral_reads |>
  filter(Background.sample != "Neg_control") |>
  filter(Background.sample != "Msp_p6") |>
  ggplot(aes(x = Viral.load, y = prop_viral, colour = genus)) +
  geom_point() +
  geom_smooth(aes(group = genus, linetype = genome_structure), se = FALSE) +
  facet_grid(target ~ Background.sample, labeller = as_labeller(facet_names)) +
  theme_few() + 
  scale_x_log10() +
  scale_y_log10() +
    scale_linetype_manual(values=c("solid", "dotted"))+ 
  ylab("Proportion of viral reads") +
  xlab("Viral load (gc/ml)") + 
  scale_color_manual(values = cols) +
    theme(
    axis.title.x = element_text(size = 12),
    # axis.text.x = element_text(angle = 30, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  )

dedup_prop_all <-
  dedup_viral_reads |>
  filter(Background.sample != "Neg_control") |>
  filter(Background.sample != "Msp_p6") |>
  ggplot(aes(x = Viral.load, y = prop_total, colour = genus)) +
  geom_point() +
  geom_smooth(aes(group = genus, linetype = genome_structure), se = FALSE) +
  facet_grid(target ~ Background.sample, labeller = as_labeller(facet_names)) +
  theme_few() + 
  scale_x_log10() +
  scale_y_log10(limits=c(5e-8,1)) +
  ylab("Proportion of total reads") +
  xlab("Viral load (gc/ml)") + 
  scale_linetype_manual(values=c("solid", "dotted"))+ 
  scale_color_manual(values = cols) +
    theme(
    axis.title.x = element_text(size = 12),
    # axis.text.x = element_text(angle = 30, hjust = 1),
    axis.title.y = element_text(size = 12),
    axis.text.y = element_text(hjust = 1),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  )
